Structured Versus Decorated Cospans

### 2022-03-10 ResponseToReviews.tex

\documentclass[reqno]{amsart}

\usepackage{amssymb,amsmath,stmaryrd,txfonts,mathrsfs,amsthm}%,undertilde}
\usepackage{comment}
\usepackage[neveradjust]{paralist}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage[outline]{contour}
\contourlength{1.2pt}
\usepackage{tikz}
\usetikzlibrary{intersections,arrows.meta,calc,quotes,math,decorations.pathreplacing,decorations.markings,cd,arrows,positioning,fit,matrix,
shapes.geometric,external,decorations.pathmorphing,backgrounds,circuits,circuits.ee.IEC,shapes}
\usepackage[a4paper,top=2cm,bottom=2cm,inner=3cm,outer=3cm]{geometry}
\usepackage[foot]{amsaddr}
\usepackage{graphicx}
\usepackage{stackrel}

% math symbols

\newcommand*{\graysquare}{\textcolor{lightgray}{\blacksquare}}

\newcommand{\double}[1]{\mathbf{\mathbb #1}}
\newcommand{\lCsp}{\double{Csp}}
\newcommand{\lCospan}{\double{Cospan}}
\newcommand{\lOpen}{\double{Open}}
\newcommand{\Fr}{\double{Fr}}
\newcommand{\lA}{\double{A}}
\newcommand{\lB}{\double{B}}
\newcommand{\lC}{\double{C}}
\newcommand{\lD}{\double{D}}
\newcommand{\lE}{\double{E}}
\newcommand{\lF}{\double{F}}
\newcommand{\lG}{\double{G}}
\newcommand{\lH}{\double{H}}
\newcommand{\lR}{\double{R}}
\newcommand{\lX}{\double{X}}
\newcommand{\lY}{\double{Y}}

@@

\section{Our Answer}

\begin{enumerate}

\item As the only point against, I feel there is a growing number of “cospan” articles. The present work seems like it could serve as a comparison of 
all of 
these, but perhaps that comparison could be more explicit and detailed: what is it done in each one of these “cospan” articles? is there anything 
that 
is not already explained in this one? If some of the articles about decorated cospans were found to contain errors, is this the only construction of 
decorated cospans that solves these errors?

{\bf The present work reviews all previous work on decorated and structured cospans in Section 6.  As we mention, our previous paper ``Structured 
cospans'' fixed the errors in previous work using decorated cospans by using structured cospans instead.   Here we describe how the new improved 
decorated cospans can also fix those errors.     There may be even more ways to correct these errors, but we do not know them.}

{\chris As was suggested by John at some point, would we perhaps want to add a sentence or two in the introduction, saying that indeed there are a 
number of cospan articles etc. and that in the beginning of section 6 we elaborate on those?}

 \item Lemma 2.4: when talking about the functors $F : (\mathsf{A},\otimes)\to(\mathsf{Cat},\times)$, I think sometimes it is specified that they are lax and sometimes 
it is not. Perhaps it would be clearer to always use “lax monoidal” or to just use “monoidal” to mean lax monoidal.

@@

The diagram depicting the decoration morphism $\tau$ as a natural transformation, first shown explictly on p. 10, should be moved here since it is 
implicitly used at the beginning of p. 5 to define the decoration of horizontal composites.

{\bf We have moved the natural isomorphism triangle as equation (1) in the statement of Theorem 2.1, and we have referred to it at page 10.} {\chris 
$\checkmark$} {\kenny $\checkmark$}

\item p. 9, ingredients for constructing a double functor of decorated cospan double categories.

Does the natural transformation $\theta \colon EF \Rightarrow F’ H$ have to be a natural isomorphism? Quite possibly I missed something, but I don’t see where in 
the following proofs that assumption is used.

{\bf We thank the referee for catching this important mistake!   It does not need to be an isomorphism.
In fact, in Section 6 we construct a double functor
\[      \graysquare \colon F \lCsp \to D \lCsp \]
sending any open Petri net with rates to its corresponding open dynamical system, and we do this
using a monoidal natural transformation $\theta$ that is \emph{not} an isomorphism.  We had mistakenly
written that it was; we've fixed this now.}

@@

{\kenny Yes, originally it was an identity. Structured cospans has similar squares for its maps, but those ones are required to be invertible. In my 
thesis, I was going to try to come up with a recipe for turning those squares into these ones, so I made these ones invertible, too, but never 
actually got around to this.}

{\chris I see! So for maps of structured cospans, invertibility is actually essential?}

{\kenny Yep, we needed certain maps $L' F \Rightarrow F' L$ (using structured cospan letters) to be invertible. We also built those maps by hand, though, and here, we're using Shulman's mystical machine to build these ones. I'm not sure what happens or is required when building maps of structured cospans using Shulman's machine...}

{\john  As Christina pointed out on Zulip, the $\theta : EF \Rightarrow F'H$ on page 26, where we are
constructing a map from open Petri nets with rates to open dynamical systems, is \emph{not} an
isomorphism.  I changed ``natural isomorphism'' to ``natural transformation'' at three points on page 26 --- 
{\bf please help make sure we catch them all!}

Also, I'd better change the remark about  $\theta: EF \Rightarrow F'H$  on page 9, and
 in the statement of Theorem 2.5 --- these are two cases where we called it a ``natural 
isomorphism''.    I'll do this now: I'll change it to a ``natural transformation''.

I've thanked the referee profusely for catching this problem --- check out my response in boldface
above, and if you're happy, we can check this one off!}

### 2022-03-10 cospans_new.tex
updated date
changed theta to natural TRANSFORMATION in 2 places

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/03/07 - dealing with referee's comments

@@

\item a natural isomorphism $\theta \maps EF \Rightarrow F'H$: 

@@

\begin{thm}
\label{thm:functoriality}
Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, \maps (\A,+) \to (\Cat,\times)$ and $F' \maps (\A',+) \to 
(\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and 
a monoidal natural isomorphism $\theta$ as in the following diagram:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\scriptstyle\Downarrow\theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[below]{$F'$} (D);
\end{tikzpicture}
\] 
we obtain a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.  If $F, F'$ and $E$ are symmetric, then $\lH \maps F\lCsp \to F'\lCsp$ is a symmetric monoidal double functor. 
\end{thm}

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/03/10 - dealing with referee's comments

@@

\item a natural transformation $\theta \maps EF \Rightarrow F'H$: 

@@

\begin{thm}
\label{thm:functoriality}
Given categories $\A$ and $\A'$ with finite colimits, lax monoidal pseudofunctors $F, \maps (\A,+) \to (\Cat,\times)$ and $F' \maps (\A',+) \to 
(\Cat,\times)$, a finite colimit preserving functor $H \maps \A \to \A'$, a lax monoidal pseudofunctor $E \maps (\Cat,\times) \to (\Cat,\times)$ and 
a monoidal natural transformation $\theta$ as in the following diagram:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\scriptstyle\Downarrow\theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[below]{$F'$} (D);
\end{tikzpicture}
\] 
we obtain a double functor $\lH \maps F\lCsp \to F'\lCsp$ defined as above.  If $F, F'$ and $E$ are symmetric, then $\lH \maps F\lCsp \to F'\lCsp$ is a symmetric monoidal double functor. 
\end{thm}
